---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "README-"
)

options(stringsAsFactors = FALSE)

```

albopop - Generate RSS feeds 

The following functions are implemented:

- `ap_parse_page`: parse a page
- `ap_build_rss`: build an rss feed
- `ap_build_msg`: build a message to send with Telegram and Twitter
- `ap_send_telegram`: send a message with Telegram 

### News

- Version 0.1.1 : added `noindex` meta tag ([#90 in aborruso/albo-pop ](https://github.com/aborruso/albo-pop/issues/90)) 
- Version 0.1.0 released

### Installation

```{r eval=FALSE}
devtools::install_github("patperu/albopop")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=160)
```

### Usage

```{r}
library("albopop")
library("rvest")

# current version
packageVersion("albopop")
```
The function `ap_parse_page` parse the content for different sites. The parameter `site` specify the type of input. Currently four providers are supported:

   - `JCityGov` [Comune di Medesano](http://195.62.183.230/web/trasparenza/papca-ap/-/papca/igrid/166/177)
   - `mapweb` [Comune di Lovere](http://www.mapweb.it/lovere/albo/albo_pretorio.php)
   - `saga` [Comune di Bellusco](http://pubblicazioni1.saga.it/publishing/AP/index.do?org=bellusco)
   - `studiok` [Comune di Lu](http://albo.studiok.it/lu/albo/)

To parse the announcements for the [Comune di Lu](http://albo.studiok.it/lu/albo/)

```{r eval = TRUE}
res <- ap_parse_page(url = "http://albo.studiok.it/lu/albo", site = "studiok")
str(res)
```

The function `ap_build_rss` generates an RSS feed and writes a simple XML file in the local default directory `feed`. The input must contain at least three columns named `Oggetto`, `Inizio` and `link`. To write the file "Lu.xml":

```{r eval=TRUE, include = TRUE}
ap_build_rss(res, 
             rss_title = "Comune di Lu", 
             rss_link  = "http://albo.studiok.it/lu/albo", 
             rss_file  = "Lu.xml")
```

### Send notifications with Telegram and Twitter

Before sending notifications it is necessary to set the appropriate Tokens for bit.ly, Telegram and Twitter.

```{r eval = FALSE, include = TRUE}
library(urlshorteneR)

bitly_token <- bitly_auth(key    = Sys.getenv("bitly_key"),
                          secret = Sys.getenv("bitly_secret"))

res <- data.frame(Comune = "Alseno.xml",
                  title  = "[53 / 2016] AVVISO DI AVVENUTO RILASCIO DI...",
                  pubDate = "2016-02-20",
                  link =  "http://albo.studiok.it/alseno/albo/dettaglio.php?id=MES00000000532016",
                  stringsAsFactors = FALSE)

res_msg <- ap_build_msg(res)
str(res_msg)
# 'data.frame':	1 obs. of  7 variables:
# $ Comune      : chr "Alseno.xml"
# $ title       : chr "[53 / 2016] AVVISO DI AVVENUTO RILASCIO DI..."
# $ pubDate     : chr "2016-02-20"
# $ link        : chr "http://albo.studiok.it/alseno/albo/dettaglio.php?id=MES00000000532016"
# $ blyurl      : chr "http://bit.ly/214xeQJ"
# $ msg_Telegram: chr "[53 / 2016] AVVISO DI AVVENUTO RILASCIO DI..., http://bit.ly/214xeQJ"
# $ msg_Twitter : chr "[53 / 2016] AVVISO DI AVVENUTO RILASCIO DI..., http://bit.ly/214xeQJ"
```

The function `ap_build_msg` adds three columns to the input:

 - `blyurl`: The shortened URL
 - `msg_Telegram`: The Telegram message, contains the `title`, the `blyurl` and the `date`
 - `msg_Twitter`: The Twitter message, contains the `title` (truncated to 100 characters), the `blyurl` and the `date`

```{r, eval = FALSE, include = TRUE}
ap_send_telegram(res_msg$msg_Telegram, "LU_TOKEN", "LU_CHAT_ID")
```

To send a notification with Twitter 

```{r eval = FALSE, include = TRUE}
library('twitteR')

setup_twitter_oauth(Sys.getenv("twitter_api_key"),
                    Sys.getenv("twitter_api_secret"),
                    Sys.getenv("twitter_access_token"),
                    Sys.getenv("twitter_access_token_secret"))

tweet(res_msg$msg_Twitter)
```

### Meta

* Please [report any issues or bugs](https://github.com/patperu/albopoo/issues).
* License: MIT

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
